---
title: "FA1"
author: "Frances Aneth Rosales"
date: "`r Sys.Date()`"
output:
  html_document:
    css: FA1.css

---


```{r files_insert}
library(ggplot2)
library(tidyr)
library(broom)
library(readxl)

whrdata <- read_excel("C:\\Users\\asus\\Documents\\ALL FEU FILES\\FEU FOLDER 6\\LINEAR MODEL\\FA1\\WHR2023.xlsx")

colnames(whrdata) <- c("Country_name", "Index", "Healthy_life_expectancy", "Freedom_to_make_life_choices", "Generosity", "Perceptions_of_corruption","Ladder_score_in_Dystopia","Log_GDP_per_capita")

View(whrdata)
```
<br><br>

# 1. Construct a SLM and try to assess the movement in the Happiness Index of a country if life expectancies at  birth changes
```{r 1.1}
happiness_vs_corruption <- lm(Index ~ Perceptions_of_corruption, data = whrdata)

summary_corruption <- summary(happiness_vs_corruption)
summary_corruption
```
<br><br>

# 2. Determine the $\beta_{0}$ and the $\beta_{1}$
```{r 1.2}
beta0_corruption <- coef(happiness_vs_corruption)[1]
print(paste("Beta0:", beta0_corruption))

beta1_corruption <- coef(happiness_vs_corruption)[2]
print(paste("Beta1:", beta1_corruption))
```
<br><br>

# 3. Determine the variance of $\beta_{0}$ and the $\beta_{1}$
```{r 1.3}

var_beta0_corruption <- vcov(happiness_vs_corruption)[1, 1]
print(paste("Variance of Beta0:", var_beta0_corruption))

var_beta1_corruption <- vcov(happiness_vs_corruption)[2, 2]
print(paste("Variance of Beta1:", var_beta1_corruption))

```
<br><br>

# 4. Determine the mean value of $e_{i}$
```{r 1.4}

mean_residuals_corruption <- mean(residuals(happiness_vs_corruption))
print(paste("Mean value of e_i:", mean_residuals_corruption))

```
<br><br>

# 5. Determine the Coefficient of Determination
```{r 1.5}
r_squared_corruption <- summary_corruption$r.squared
print(paste("Coefficient of Determination:", r_squared_corruption))

```
<br><br>

# 6. Write the final SL Model
```{r 1.6}


finalmodel_corruption <- paste("Happiness Index vs Perception of Corruption =", round(beta0_corruption, 3), "+", round(beta1_corruption, 3), "* Perceptions of Corruption", "+",(mean_residuals_corruption) )

print(paste(" Final SL Model: ", finalmodel_corruption))
```

<br><br>

# 7. Explain the result of your model

<h4>  

$\beta_{0}$   <br>
As we determine the $\beta_{0}$ accumulated <b> 7.7450 </b>, Since the Perception of Corruption is unlikely to be exactly zero in real-life circumstances, it may not have a clear practical interpretation.


$\beta_{1}$ <br>
Since this is the predicted shift in the Happiness Index in response to a rise of one unit in the perception of corruption. <br>
In our situation, it is anticipated that the Happiness Index will drop by <b> 3.0400 </b> units for every unit that the Perception of Corruption rises.



Therefore, the bad indication of shows a negative correlation between the Happiness Index and the Perception of Corruption. The Happiness Index tends to decrease when corruption occurs to happen.

However, it is also needed to consider that the residual<b> standard error (1.009) </b> provides an indication of the normal residual size and a measure of the Happiness Index variability not explained by the Perception of Corruption.
</h4>


<br><br>

# 8. Prepare some visualizations as part of your explanation
```{r 1.8}
library(ggplot2)
library(cowplot)

ggplot(whrdata, aes(x = Perceptions_of_corruption, y = Index)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "violet") +
  labs(title = "Happiness Index vs Perceptions of Corruption",
       x = "Perceptions of Corruption",
       y = "Happiness Index",
       caption = "Figure 1.1") +
  theme(plot.caption = element_text(hjust = 0.5))  

  
```
<h4>
As assumed, the index of Happiness indeed decreases as the Perception of Corruption increases as shown in Figure 1.1.  
</h4>



<br><br>
<br><br>

# 1. Construct a SLM and try to assess the movement in the Happiness Index of a country if life expectancies at  birth changes
```{r 2.1}
happiness_vs_life_expectancy <- lm(Index ~ Healthy_life_expectancy, data = whrdata)
summary_life_expectancy <- summary(happiness_vs_life_expectancy)
summary_life_expectancy
```
<br><br>

# 2. Determine the $\beta_{0}$ and the $\beta_{1}$
```{r 2.2}
beta0_life_expectancy <- coef(happiness_vs_life_expectancy)[1]
beta1_life_expectancy <- coef(happiness_vs_life_expectancy)[2]
print(paste("Beta0:", beta0_life_expectancy))
print(paste("Beta1:", beta1_life_expectancy))
```
<br><br>

# 3. Determine the variance of $\beta_{0}$ and the $\beta_{1}$
```{r 2.3}

var_beta0_life_expectancy <- vcov(happiness_vs_life_expectancy)[1, 1]
var_beta1_life_expectancy <- vcov(happiness_vs_life_expectancy)[2, 2]
print(paste("Variance of Beta0:", var_beta0_life_expectancy))
print(paste("Variance of Beta1:", var_beta1_life_expectancy))

```
<br><br>

# 4. Determine the mean value of $e_{i}$
```{r 2.4}
mean_residuals_life_expectancy <- mean(residuals(happiness_vs_life_expectancy))
print(paste("Mean value of e_i:", mean_residuals_life_expectancy))

```
<br><br>

# 5. Determine the Coefficient of Determination
```{r 2.5}
r_squared_life_expectancy <- summary_life_expectancy$r.squared
print(paste("Coefficient of Determination:", r_squared_life_expectancy))

```
<br><br>

# 6. Write the final SL Model
```{r 2.6}
final_model_life_expectancy <- paste("Happiness Index vs Life Expectancy =", round(beta0_life_expectancy, 3), "+", round(beta1_life_expectancy, 3), "* Healthy Life Expectancy ","+",(mean_residuals_life_expectancy) )
print(paste(" Final SL Model ", final_model_life_expectancy))

```

<br><br>

# 7. Explain the result of your model

<h4>  

$\beta_{0}$  <br>
As we determine the $\beta_{0}$ accumulated <b> −4.09971 </b>, Since the Life Expectancy is also not possible to be exactly zero in real-life circumstances,interpreting data using Simple Linear Model would not be practical for this scenario.


$\beta_{1}$ <br>
This on the otherhand predicted the shifting of Happiness Index corresponds to the Life Expectancy from our Data Base. <br>
We can now see as Happiness Index will increases by <b>  0.14845 </b> units whenever the Life Expectancy increases, then it pertains that the result has a correlates proportionally with the index. 

Therefore, now we can see a good correlation of proportion increment of Life Expectancy and the Happiness Index. 

However, just we assumed on our preceding assumption on Happiness Index vs Perception of Corruption, our data accumulated a <b> standard error of (0.7627) </b> thus we cannot also say that the Happiness Index has an indeed correlation between Life Expectancy.
</h4>


<br><br>

# 8. Prepare some visualizations as part of your explanation
```{r 2.8}
library(ggplot2)
library(cowplot)

ggplot(whrdata, aes(x = Healthy_life_expectancy, y = Index)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "violet") +
  labs(title = "Happiness Index vs Life Expectancy",
       x = "Life Expectancy",
       y = "Happiness Index",
       caption = "Figure 2.1") +
  theme(plot.caption = element_text(hjust = 0.5))
```
<h4>
As assumed, the index of Happiness indeed increases as the Life Expectancy increases as shown in Figure 2.1.  
</h4>



































































